Pottery decor as networks on the Middle Niger

### 2024-06-07 analysis/paper/paper.Rmd
figure changes

# Fractured and extrapolated diversity of Doupwil
  i <- decors_abs[,c(4)]|> 
 iNEXT(q=c(0), datatype="abundance")
 ggiNEXT(i, type=1, facet.var="Assemblage")+
  labs(title = "Doupwil")

# Fractured and extrapolated diversity of Jenne-jeno
 i <- decors_abs[,c(8)]|> 
 iNEXT(q=c(0), datatype="abundance")
  ggiNEXT(i, type=1, facet.var="Assemblage")+
  labs(title = "Jenne-jeno")

@@

ggraph(decor_20, layout = "nicely") +
  geom_node_point(aes(size = centrality_eigen())) +
  geom_edge_fan(color = "grey", alpha = 0.8, aes(edge_width = weight)) +
  scale_edge_width(range = c(0.2, 3)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  theme_graph() +
  labs(size = "eigenvector centrality")
```

@@

```{r backbone-betweenness, fig.cap="Binary backbone at alpha = 0.15 showing betweenness centralities"}
ggraph(decor_20, layout = "nicely") +
  geom_node_point(aes(size = centrality_betweenness())) +
   geom_edge_fan(color = "grey", alpha = 0.8, aes(edge_width = weight)) +
  scale_edge_width(range = c(0.2, 3)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  theme_graph() +
  labs(size = "betweenness centrality")
```

@@

#plot
ggraph(early_flat_bb, layout = "stress") +
  geom_node_point(aes(size = centrality_betweenness())) +
  geom_edge_fan(aes(width = weight), color = "grey", alpha = 0.8) +
  scale_edge_width(range = c(0.2, 3)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  theme_graph()
```

>>>>

# Fractured and extrapolated diversity of Doupwil
  i <- decors_abs[,c(4)]|> 
 iNEXT(q=c(0), datatype="abundance")
 p1 <- ggiNEXT(i, type=1, facet.var="Assemblage")+
  labs(title = "Doupwil")

# Fractured and extrapolated diversity of Jenne-jeno
 i <- decors_abs[,c(8)]|> 
 iNEXT(q=c(0), datatype="abundance")
 p2 <-  ggiNEXT(i, type=1, facet.var="Assemblage")+
  labs(title = "Jenne-jeno")

@@

ggraph(decor_20, layout = "nicely") +
  geom_edge_fan(color = "grey", alpha = 0.8, aes(edge_width = weight)) +
   geom_node_point(aes(size = centrality_eigen(weights = weight))) +
  scale_edge_width(range = c(0.2, 3)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  theme_graph() +
  labs(size = "eigenvector centrality")
```

@@

```{r backbone-betweenness, fig.cap="Binary backbone at alpha = 0.15 showing betweenness centralities"}
ggraph(decor_20, layout = "nicely") +
   geom_edge_fan(color = "grey", alpha = 0.8, aes(edge_width = weight)) +
    geom_node_point(aes(size = centrality_betweenness(weights = weight))) +
  scale_edge_width(range = c(0.2, 3)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  theme_graph() +
  labs(size = "betweenness centrality")
```

@@

#plot
ggraph(early_flat_bb, layout = "stress") +
  geom_edge_fan(aes(width = weight), color = "grey", alpha = 0.8) +
    geom_node_point(aes(size = centrality_betweenness())) +
  scale_edge_width(range = c(0.2, 3)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  theme_graph()+
  labs(size = "betweenness centrality")
```
